Introduction to Markov state modeling with the PyEMMA software [Article v\versionnumber]

### 2018-11-29 manuscript/manuscript.tex
chapman-kolmogorov > ck

\begin{figure}[ht]
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
The solid lines refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line (marking equality of timescale and lag time) with grey area indicates the timescale horizon below which the MSM cannot resolve processes.
As implied timescales are well-converged at $\tau=\SI{0.5}{\nano\second}$, this lag time is chosen for subsequent MSM estimation.
(b)~Chapman-Kolmogorov test computed using an MSM estimated with lag time $\tau=\SI{0.5}{\nano\second}$ assuming~5 metastable states.
Predictions from this model agree with higher lag time estimates within confidence intervals.
Implied timescales convergence as well as a passing Chapman-Kolmogorov test are a necessary condition in MSM validation.
In both panels, the (non-grey) shaded areas indicate~\SI{95}{\percent} confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}

@@

To test the validity of our MSM, we perform a Chapman-Kolmogorov (CK) test.
Visualizing the full transition probability matrix $T$ is difficult;
we therefore coarse-grain $T$ into a smaller number of metastable states before performing the test.
An appropriate number of metastable states can be chosen by identifying a relatively large gap in the ITS plot.
For this analysis, we chose five metastable states.
The CK test (Fig.~\ref{fig:its-and-ck}b) shows that predictions from our MSM (blue-dashed lines)
agrees well with MSMs estimated with longer lag times (black-solid lines)
Thus, the CK test confirms that five metastable states is an appropriate choice
and shows that the MSM we have estimated at lag time $\tau=\SI{0.5}{\nano\second}$ indeed predicts the
long-timescale behavior of our system within error (blue/shaded area).

>>>>

\begin{figure}[ht]
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
The solid lines refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line (marking equality of timescale and lag time) with grey area indicates the timescale horizon below which the MSM cannot resolve processes.
As implied timescales are well-converged at $\tau=\SI{0.5}{\nano\second}$, this lag time is chosen for subsequent MSM estimation.
(b)~CK test computed using an MSM estimated with lag time $\tau=\SI{0.5}{\nano\second}$ assuming~5 metastable states.
Predictions from this model agree with higher lag time estimates within confidence intervals.
Implied timescales convergence as well as a passing CK test are a necessary condition in MSM validation.
In both panels, the (non-grey) shaded areas indicate~\SI{95}{\percent} confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}

@@

To test the validity of our MSM, we perform a CK test.
Visualizing the full transition probability matrix $T$ is difficult;
we therefore coarse-grain $T$ into a smaller number of metastable states before performing the test.
An appropriate number of metastable states can be chosen by identifying a relatively large gap in the ITS plot.
For this analysis, we chose five metastable states.
The CK test (Fig.~\ref{fig:its-and-ck}b) shows that predictions from our MSM (blue-dashed lines)
agrees well with MSMs estimated with longer lag times (black-solid lines)
Thus, the CK test confirms that five metastable states is an appropriate choice
and shows that the MSM we have estimated at lag time $\tau=\SI{0.5}{\nano\second}$ indeed predicts the
long-timescale behavior of our system within error (blue/shaded area).
